---
title: "BUAN6357_AirBnBProject_Jadhav"
output: 
  html_document: 
    toc: yes
---

__Load required packages:__
```{r loadpackages, message=FALSE}
#Load packages
if (!require('caret')) {
  install.packages('caret')
}
if (!require('ggplot2')) {
  install.packages('ggplot2')
}
if (!require('rworldmap')) {
  install.packages('rworldmap')
}
if (!require('gridExtra')) {
  install.packages('gridExtra')
}
if (!require('car')) {
  install.packages('car')
}
if (!require('xgboost')) {
  install.packages('xgboost')
}
if (!require('Ckmeans.1d.dp')) {
  install.packages('Ckmeans.1d.dp')
}
if (!require('tidyr')) {
  install.packages('tidyr')
}
if (!require('readr')) {
  install.packages('readr')
}
if (!require('dplyr')) {
  install.packages('dplyr')
}
if (!require('e1071')) {
  install.packages('e1071')
}
if (!require('caTools')) {
  install.packages('caTools')
}
if (!require('rpart')) {
  install.packages('rpart')
}
if (!require('randomForest')) {
  install.packages('randomForest')
}
if (!require('GGally')) {
  install.packages('GGally')
}
if (!require('stringr')) {
  install.packages('stringr')
}
if (!require('e1071')) {
  install.packages('e1071')
}
if (!require('class')) {
  install.packages('class')
}
if (!require('corrplot')) {
  install.packages('corrplot')
}

```

__Load the data set:__
```{r}
#Load dataset
df <- read.csv("train_users_2.csv")

#Basic data exploration
cat("Dimension:")
dim(df)

cat("\n","Names of columns:",'\n')
names(df)

cat("\n","Structure of dataset:",'\n')
str(df)

cat("\n","Summary:",'\n')
summary(df)

cat("\n","First look at the dataset:",'\n')
head(df)
```

__Performing PCA:__
```{r}

#PCA to check for features having max variance
ZV <- nearZeroVar(df, saveMetrics = TRUE)
ZV

```

__Analyzing user's age:__
```{r}
#Analyzing user's age
cat("Summary of user's age","\n")
summary(df$age)
qplot(x = age, data = df, binwidth = 1,fill = df$gender, facets = .~gender, xlim = c(18,75), main = "Distribution of age across genders")+ guides(fill=guide_legend(title="Gender"))

cat("\n","Summary of user's age across genders","\n")
by(df$age, df$gender, summary)
```

```{r}
#Age by a Destination Country
by(df$age, df$country_destination, summary)

ggplot(df, aes(country_destination, age)) +
  geom_boxplot(aes(), fill ="red") + 
  ylim(25,50)+ggtitle("Distribution of age across country destinations")+xlab("Country destination")

ggplot(df, aes(age)) +
  geom_histogram(binwidth = 1, color = 'black', fill = '#099DD9') +
  xlim(18,75) +
  facet_wrap(~country_destination, ncol = 3, scales = "free")+ggtitle("Distribution of age across country destinations")

ggplot(df, aes(age)) +
  geom_histogram(binwidth = 1, color = 'black', fill = '#099DD9') +
  geom_histogram(data=subset(df,age==20), color = "black", fill="red", binwidth = 1) +
  scale_x_continuous(limits = c(15, 25), breaks = seq(15, 25, 1)) +
  facet_wrap(~country_destination, ncol = 3, scales = "free")+ggtitle("Focusing on age group of 20 year old travellers")
```

```{r}
#Age on a Map of Destination Countries
df.age.summ <- summarise(group_by(df, country_destination), 
                         medianAge = median(age, na.rm = TRUE),
                         meanAge = mean(age, na.rm = TRUE),
                         sdAge = sd(age, na.rm = TRUE)
)
capture.output(spdf <- joinCountryData2Map(subset(df.age.summ, country_destination != "other" & country_destination != "NDF"),
                            joinCode="ISO_A2", 
                            nameJoinColumn="country_destination",
                            verbose = FALSE), file = 'NUL'
)
mapCountryData(spdf, 
               nameColumnToPlot="medianAge", 
               catMethod="fixedWidth", 
               numCats=3,
               mapTitle = "Median Age of Airbnb Users"
)
mapCountryData(spdf, 
               nameColumnToPlot="meanAge", 
               catMethod="fixedWidth", 
               numCats=3,
               mapTitle = "Mean Age of Airbnb Users"
)
df.age.summ2 <- summarise(group_by(subset(df, age<76 & age>17), country_destination),
                          meanAge = mean(age, na.rm = TRUE),
                          sdAge = sd(age, na.rm = TRUE))

capture.output(spdf2 <- joinCountryData2Map(subset(df.age.summ2, 
                                    country_destination != "other" & country_destination != "NDF"),
                             joinCode="ISO_A2", 
                             nameJoinColumn="country_destination",
                            verbose = FALSE), file = 'NUL'
)
mapCountryData(spdf2, 
               nameColumnToPlot="meanAge", 
               catMethod="fixedWidth", 
               numCats=10,
               mapTitle = "Mean Age of Airbnb Users in the Age-Group 18-75"
)
```

__Analyzing user's Gender:__
```{r}
#Analysing Users Gender
ggplot(df, aes(x = gender)) + 
  geom_bar(fill ="#E69F00")+
  ggtitle("Overall gender distribution")

df.gender <- spread(df, gender, age)
colnames(df.gender)[15] <- "unknown"
df.gender.summ <- summarise(group_by(df.gender, country_destination), 
                            countF = sum(!is.na(FEMALE)),
                            countM = sum(!is.na(MALE)),
                            countO = sum(!is.na(OTHER)),
                            countUn = sum(!is.na(unknown)),
                            total_with_NA = n())
capture.output(spdf <- joinCountryData2Map(subset(df.gender.summ, 
                                   country_destination != "other" &
                                     country_destination != "NDF"), 
                            joinCode="ISO_A2", 
                            nameJoinColumn="country_destination",
                            verbose = FALSE), file = 'NUL'
)
df_map <- subset(spdf@data, !is.na(country_destination))
par(mai= c(0,0,0.3,0),
    xaxs = "i",
    yaxs = "i")
mapPies(dF =df_map,
        nameX="LON",
        nameY="LAT",
        nameZs =c("countF",
                  "countM",
                  "countO",
                  "countUn") ,
        zColours=c("red",
                   "green",
                   "yellow",
                   "blue"),
        oceanCol = "lightblue",
        landCol = "wheat",
        addSizeLegend=T,
        addCatLegend=F,
        mapRegion="world",
        xlim=c(-181,181),
        ylim=c(-81,80),
        symbolSize = 2)

title(main=paste("Number of Airbnb Users by Gender"),
      cex=3)

legend(-180.1590,80,
       legend=c("Female",
                "Male",
                "Other",
                "Unknown"),
       col=c("red",
             "green",
             "yellow",
             "blue"),
       pch=16,
       cex=0.8,
       pt.cex=1.5,
       bty="o",
       box.lty=0,
       horiz = F,
       bg="#FFFFFF70")
```

__Analysing Dates and Times:__
```{r}

#Analysing Dates and Times
df$date_account_created <- as.character(df$date_account_created)
df$date_first_booking <- as.character(df$date_first_booking)
df$date_first_booking <- ifelse(df$date_first_booking == "", df$date_account_created, df$date_first_booking)
df$date_account_created <- as.Date(df$date_account_created)
df$date_first_booking <- as.Date(df$date_first_booking)

summary(df$date_account_created)
summary(df$date_first_booking)

df$month_acc_created <- factor(format(df$date_account_created, format = "%B"), 
                               levels = c("January", "February", "March", "April", 
                                          "May", "June", "July", "August", "September",
                                          "October", "November", "December")) 
df$day_acc_created <- factor(format(df$date_account_created, format = "%d")) 
df$dac_weekday <- factor(format(df$date_account_created, format = "%A"), 
                         levels = c("Monday", "Tuesday", "Wednesday", 
                                    "Thursday", "Friday", "Saturday", 
                                    "Sunday"))


df$month_first_book <- factor(format(df$date_first_booking, format = "%B"), 
                              levels = c("January", "February", "March", "April", 
                                         "May", "June", "July", "August", "September",
                                         "October", "November", "December")) 
df$day_first_book <- factor(format(df$date_first_booking, format = "%d")) 
df$weekday_first_book <- factor(format(df$date_first_booking, format = "%A"), 
                                levels = c("Monday", "Tuesday", "Wednesday", 
                                           "Thursday", "Friday", "Saturday", 
                                           "Sunday"))
```

__Analysing distribution of bookings:__
```{r}
#Monthly distribution of bookings
tb<-table(df$month_first_book)
tb_df<-as.data.frame(tb)
colnames(tb_df) <- c("Month","Freq")
tb_df


qplot(x = month_first_book, data = df, fill = df$month_first_book, main = "Monthly bookings", xlab = "Month of first booking")+guides(fill=guide_legend(title="Month of booking"))

ggplot(subset(df, country_destination != "NDF"), aes(x = month_first_book)) +
  geom_bar(data=subset(df,country_destination != "NDF" &
                         month_first_book %in% c("June", "May")),
           color = "black", fill="green") +
  geom_bar(data=subset(df,country_destination != "NDF" &
                         month_first_book %in% c("January", "February", "March", "April", 
                                                 "July", "August", "September",
                                                 "October", "November", "December")),
           color = "black", fill="red") +
  facet_wrap(~country_destination, scales = "free")+
  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
  ggtitle("Monthly bookings across destinations") +xlab("Month of first booking")

#Booking distribution spread across month
qplot(x = day_first_book, data = df,fill = df$day_first_book, main = "Booking distribution spread across month", xlab = "Day of first booking")+guides(fill=guide_legend(title="Day of booking"))

#Country wise booking distribution spread across month
ggplot(subset(df, country_destination != "NDF"), aes(x=day_first_book)) +
  geom_bar()+
  facet_wrap(~country_destination, scales = "free")

#Booking distribution spread across week
qplot(x = weekday_first_book, data = df,fill = df$weekday_first_book, main = "Booking distribution spread across week", xlab = "Day of first booking")+guides(fill=guide_legend(title="Day of booking"))

#Country wise frequency distribution of weekly bookings
ggplot(subset(df, country_destination != "NDF"), aes(x=weekday_first_book)) +
  geom_bar(fill = "red")+
  facet_wrap(~country_destination, scales = "free")+
  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
  ggtitle("Country wise frequency distribution of weekly bookings") +xlab("Day of first booking")

```

```{r}

#Days Between Signup and First Booking
df$days_to_book <- as.numeric(df$date_first_booking - df$date_account_created)
cat("Summary:","\n")
summary(df$days_to_book)
cat("\n")
by(df$days_to_book, df$country_destination, summary)

#Days Between Signup and First Booking across destinations
ggplot(df, aes(country_destination, days_to_book)) +
  geom_boxplot()

```

__Analysing SignUp method:__
```{r}
#Analysing SignUp method
summary(df$signup_method)
signupMethod <- df$signup_method
p<-qplot(x = signup_method, data = df, fill = df$signup_method, main = "Signup method distribution", xlab = "Signup method", ylab = "Count")
p <- p + guides(fill=guide_legend(title="Signup Method"))
p

#Facebook signups across destinations
ggplot(subset(df, country_destination != "NDF" & country_destination != "US"  & signup_method == "facebook"), aes(x = signup_method)) +
  geom_bar(fill = "steelblue")+
  facet_wrap(~country_destination)+
  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
  ggtitle("Country wise frequency distribution of facebook signups") +xlab("Facebook signups")

```

__Analysing Languge:__
```{r}

#Analysing Languge
df <- within(df, language <- factor(language, 
                                    levels=names(sort(table(language),
                                                      decreasing=TRUE))))

qAll <- ggplot(subset(df, country_destination == "NDF"),
               aes(language)) +
  geom_bar(aes(fill = gender)) +
  ggtitle("Frequency distribution - NDF, All Languages")

qWoEng <- ggplot(subset(df, country_destination == "NDF" & language != "en"),
                 aes(language)) +
  geom_bar(aes(fill = gender)) +
  ggtitle("Frequency Distribution - NDF, W/o English")

grid.arrange(qAll, qWoEng, ncol = 1)

```


__Predictive modelling:__
```{r}

#Predictive modelling

#load dataset
df_train = read.csv("train_users_2.csv")

#Check for NA's
sapply(df_train,function(x) sum(is.na(x)))

# replace missing values
df_train[is.na(df_train)] <- -1

# Drop unnecessary columns
df_train = df_train[-c(which(colnames(df_train) %in% c('date_first_booking','timestamp_first_active','id')))]

# split date_account_created in year, month and day
dac = as.data.frame(str_split_fixed(df_train$date_account_created, '-', 3))
df_train['dac_year'] = dac[,1]
df_train['dac_month'] = dac[,2]
df_train['dac_day'] = dac[,3]
df_train$date_account_created <- as.Date(as.character(df_train$date_account_created) )
df_train$dac_weekday <- factor(format(df_train$date_account_created, format = "%A"), 
                               levels = c("Monday", "Tuesday", "Wednesday", 
                                          "Thursday", "Friday", "Saturday", 
                                          "Sunday"))
df_train = df_train[,-c(which(colnames(df_train) %in% c('date_account_created')))]

```

```{r}

# Categorizing age in 9 groups
df_train[df_train$age < 14 | df_train$age > 100,'age'] <- -1
df_train$age <- findInterval(df_train$age, c(20,30,40,50,60,70,80,90))
table(df_train$age)

```

```{r}

#Detaching target variable from dataset for analysis
labels = df_train['country_destination']
df_train = df_train[-grep('country_destination', colnames(df_train))]

```

```{r}

# Data manipulation to combine low observed values into one category before creating dummies
df_train$affiliate_provider <- car::recode(df_train$affiliate_provider, "'baidu' = 'other';'daum' = 'other';'naver' = 'other';'wayn' = 'other';'yandex' = 'other';'facebook-open-graph' = 'facebook';'bing' = 'other';'email-marketing' = 'other';'gsp' = 'other';'meetup' = 'other';'padmapper' = 'other';'vast' = 'other';'yahoo' = 'other'")

df_train$language<- car::recode(df_train$language,"'it'='other'; 'th'='other'; 'ru'='other'; 'pt'='other'; 'ja'='other'; 'sv'='other'; 'nl'='other'; 'tr'='other'; 'da'='other'; 'pl'='other'; 'cs'='other'; 'no'='other';'el'='other';'id'='other';'hu'='other';'fi'='other';'is'='other';'ca'='other';'hr'='other'")

df_train$first_browser <- car::recode(df_train$first_browser,"'Android Browser' = 'other';'AOL Explorer' = 'other';'Apple Mail' = 'other';'Arora' = 'other';'Avant Browser' = 'other';'BlackBerry Browser' = 'other';'Camino' = 'other';'Chrome Mobile' = 'Chrome';'Chromium' = 'Chrome';'CometBird' = 'other';'Comodo Dragon' = 'other';'Conkeror' = 'other';'CoolNovo' = 'other';'Crazy Browser' = 'other';'Epic' = 'other';'Flock' = 'other';'Google Earth' = 'other';'Googlebot' = 'other';'IceDragon' = 'other';'IceWeasel' = 'other';'IE Mobile' = 'IE';'Iron' = 'other';'Kindle Browser' = 'other';'Maxthon' = 'other';'Mobile Firefox' = 'Firefox';'Mozilla' = 'other';'NetNewsWire' = 'other';'OmniWeb' = 'other';'Opera' = 'other';'Opera Mini' = 'other';'Opera Mobile' = 'other';'Outlook 2007' = 'other';'Pale Moon' = 'other';'Palm Pre web browser' = 'other';'PS Vita browser' = 'other';'RockMelt' = 'other';'SeaMonkey' = 'other';'Silk' = 'other';'SiteKiosk' = 'other';'SlimBrowser' = 'other';'Sogou Explorer' = 'other';'Stainless' = 'other';'TenFourFox' = 'other';'TheWorld Browser' = 'other';'wOSBrowser' = 'other';'Yandex.Browser' = 'other'")

df_train$first_affiliate_tracked <- car::recode(df_train$first_affiliate_tracked, " '' = 'other';'local ops' = 'other';'marketing' = 'other';'product' = 'other';'tracked-other' = 'other'" )

df_train$first_device_type <- car::recode(df_train$first_device_type,"'SmartPhone (Other)'='Other/Unknown';'Desktop (Other)' = 'Other/Unknown';'Android Phone' = 'Android';'Android Tablet' = 'Android'")

df_train$dac_weekday <- car:: recode(df_train$dac_weekday,"'Monday' = 1; 'Tuesday' = 2; 'Wednesday' = 3; 'Thursday' = 4; 'Friday' = 5; 'Saturday' = 6; 'Sunday' = 7")


# one-hot-encoding features
ohe_feats = c('gender', 'signup_method', 'signup_flow', 'language', 'affiliate_channel', 'affiliate_provider', 'first_affiliate_tracked', 'signup_app', 'first_device_type', 'first_browser')
dummies <- dummyVars(~ gender + signup_method + signup_flow + language + affiliate_channel + affiliate_provider + first_affiliate_tracked + signup_app + first_device_type + first_browser, data = df_train)
df_all_ohe <- as.data.frame(predict(dummies, newdata = df_train));'bing' = 'other'
X <- cbind(df_train[,-c(which(colnames(df_train) %in% ohe_feats))],df_all_ohe)

```

__Partition the dataset:__
```{r}

# split train and test
y <- car::recode(labels$country_destination,"'NDF'=0; 'US'=1; 'other'=2; 'FR'=3; 'CA'=4; 'GB'=5; 'ES'=6; 'IT'=7; 'PT'=8; 'NL'=9; 'DE'=10; 'AU'=11")

X <- cbind(X,y)

names(X)[names(X) == 'gender.-unknown-'] <- 'genderUnknown'
names(X)[names(X) == 'affiliate_channel.sem-brand'] <- 'affChanlsemBrand'
names(X)[names(X) == 'affiliate_channel.sem-non-brand'] <- 'affchannelsemNonBrand'
names(X)[names(X) == 'first_device_type.Mac Desktop'] <- 'first_dev_typeMacDesktop'
names(X)[names(X) == 'first_device_type.Other/Unknown'] <- 'first_dev_typOtherUnknown'
names(X)[names(X) == 'first_device_type.Windows Desktop'] <- 'first_dev_typWindDesktop'
names(X)[names(X) == 'first_browser.-unknown-'] <- 'firstbrowserUnknown'
names(X)[names(X) == 'first_browser.Mobile Safari'] <- 'first_browserMobileSafari'

ZV <- nearZeroVar(X, saveMetrics = TRUE)
ZV

X=X %>% mutate_if(is.character, as.factor)

set.seed(123)
split = sample.split(y, SplitRatio = 0.8)
training_set = subset(X, split == TRUE)
validation_set = subset(X, split == FALSE)
train_lab <- training_set$y
valid_lab <- validation_set$y
training_set = training_set[,-c(which(colnames(training_set) == c('y')))]
validation_set = validation_set[,-c(which(colnames(validation_set) == c('y')))]

```

__Utility functions:__
```{r}

# Function to compute classification error
classification_error <- function(conf_mat) {
  conf_mat = as.matrix(conf_mat)
  
  error = 1 - sum(diag(conf_mat)) / sum(conf_mat)
  
  return (error)
}

# Function to normalize data
normalize <- function(nm) {
  return ((nm - min(nm)) / (max(nm) - min(nm)))
}

```

__Predictive model using random forest algorithm:__
```{r}

#Random forest model
train_rf <- cbind(training_set,train_lab) 
train_rf <- dplyr::sample_n(train_rf, 10000)

set.seed(12345)

# Training with Random forest model
modfit.rf <- randomForest(train_lab~ . , data=train_rf,method="class")
modfit.rf

# Predicting target variable for validation set
pred_val<-predict(modfit.rf, validation_set, type = 'class')
rf_conf_mtx<-table(true=valid_lab, pred = pred_val)

# Error 
cat("\n","RF Classification Error Rate:", classification_error(rf_conf_mtx), "\n")
cat("RF Classification Accuracy Rate:",1- classification_error(rf_conf_mtx), "\n")

```

__Predictive model using SVM:__
```{r}

#SVM Model

train_svm <-cbind(training_set,train_lab) 
tune_svm <- dplyr::sample_n(train_svm, 1000)

#Grid search for hyperparameters
tuned_parameters <- tune.svm(train_lab~., data = tune_svm, gamma = 10^(-2:-1), cost = 5:10)
summary(tuned_parameters )

# training SVM model based on best performing hyperparameters
train_svm <-cbind(training_set,train_lab) 
train_svm <- dplyr::sample_n(train_svm, 10000)
mod.svm <- svm(train_lab~., data = train_svm, method="C-classification", kernal="radial", 
               gamma=0.01, cost=8)
summary(mod.svm)
pred_vald<-predict(mod.svm, validation_set)
svm_conf_mtx<-table(true=valid_lab, pred = pred_vald)

# Error 
cat("SVM Classification Error Rate:", classification_error(svm_conf_mtx), "\n")
cat("SVM Classification Accuracy Rate:",1- classification_error(svm_conf_mtx), "\n")

```

__Predictive model using KNN:__
```{r}

# KNN Model

set.seed(3333)
training_set_knn=training_set %>% mutate_if(is.factor, as.numeric)
validation_set_knn = validation_set %>% mutate_if(is.factor, as.numeric)
tknn_Norm <- as.data.frame(lapply(training_set_knn, normalize))
vknn_Norm <- as.data.frame(lapply(validation_set_knn, normalize))

train_knn <-cbind(tknn_Norm,train_lab) 
train_knn <- dplyr::sample_n(train_knn, 10000)
valid_knn <-cbind(vknn_Norm,valid_lab) 
valid_knn <- dplyr::sample_n(valid_knn, 10000)

pr <- knn(train_knn,valid_knn,cl=valid_knn$valid_lab,k=20)
knn_conf_mtx<-table(true=valid_knn$valid_lab, pred = pr)

# Error 
cat("KNN Classification Error Rate:", classification_error(svm_conf_mtx), "\n")
cat("KNN Classification Accuracy Rate:",1- classification_error(knn_conf_mtx), "\n")


```

__Predictive model using Naive Bayes algorithm:__
```{r}

# Naive Bayes model

train_NB <- cbind(training_set,train_lab)
valid_NB <- cbind(validation_set,valid_lab)

train_NB <- train_NB %>% mutate_if(is.numeric, as.factor)
valid_NB <- valid_NB %>% mutate_if(is.numeric, as.factor)
train_NB <- dplyr::sample_n(train_NB, 10000)
valid_NB <- dplyr::sample_n(valid_NB, 10000)

valid_lab_NB <- valid_NB$valid_lab
valid_NB = valid_NB[,-c(which(colnames(valid_NB) == c('valid_lab')))]

modNB <- naiveBayes(train_lab~. , data = train_NB)

summary(modNB)
print(modNB)


NB_preds <- predict(modNB, newdata = valid_NB)
NB_conf_mtx<-table(true=valid_lab_NB, pred = NB_preds)

# Error 
cat("NB Training Classification Error Rate:", classification_error(NB_conf_mtx), "\n")
cat("NB Training Classification Accuracy Rate:",1- classification_error(NB_conf_mtx), "\n")

```


__Predictive model using XGBoost algorithm:__
```{r}

# XGBoost model

## Anayse and visualize xgboost
train_xgb = X[-c(which(colnames(X) == 'y'))]
xgb <- xgboost(data = data.matrix(train_xgb), 
               label = as.numeric(as.character(y)), 
               eta = 0.1,
               max_depth = 9, 
               nround=25, 
               subsample = 0.5,
               colsample_bytree = 0.5,
               seed = 1,
               eval_metric = "merror",
               objective = "multi:softprob",
               num_class = 12,
               nthread = 3,
               missing=NA
)


model <- xgb.dump(xgb, with.stats = T)
model[1:10]
names <- dimnames(data.matrix(X))[[2]]
importance_matrix <- xgb.importance(names, model = xgb)

xgb.plot.importance(importance_matrix[1:20,])

params <- list(booster = "gbtree", objective = "multi:softprob", num_class = 12)
train_lab_xgb <-as.numeric(as.character(train_lab))
valid_lab_xgb <-as.numeric(as.character(valid_lab))
xgbcv <- xgb.cv(params = params, data = data.matrix(training_set), nrounds = 60, prediction = TRUE,
                label = train_lab_xgb, nfold = 5, showsd = TRUE, stratified = TRUE, print.every.n = 10, 
                early_stop_round = 20, maximize = FALSE)

xgb_train_preds <- data.frame(xgbcv$pred) %>% mutate(max = max.col(., ties.method = "last"), 
                                                     label = train_lab_xgb+1)
head(xgb_train_preds,20)

xgb_conf_mat <- table(true = train_lab_xgb+1, pred = xgb_train_preds$max)

# Error 
cat("XGB Training Classification Error Rate:", classification_error(xgb_conf_mat), "\n")
cat("XGB Training Classification Accuracy Rate:",1- classification_error(xgb_conf_mat), "\n")

xgb_train <- xgb.DMatrix(data = data.matrix(training_set), label = as.numeric(train_lab_xgb))
xgb_val <- xgb.DMatrix(data = data.matrix(validation_set), label = as.numeric(valid_lab_xgb))

xgb_model <- xgb.train(params = params, data = xgb_train, nrounds = 60)

xgb_val_preds <- predict(xgb_model, newdata = xgb_val)
xgb_val_out <- matrix(xgb_val_preds, nrow = 12, ncol = length(xgb_val_preds) / 12) %>% 
  t() %>%
  data.frame() %>%
  mutate(max = max.col(., ties.method = "last"), label = valid_lab_xgb + 1) 
head(xgb_val_out,20)

# Confustion Matrix
xgb_val_conf <- table(true = valid_lab_xgb + 1, pred = xgb_val_out$max)

# Error 
cat("XGB validation Classification Error Rate:", classification_error(xgb_val_conf), "\n")
cat("XGB validation Classification Accuracy Rate:",1- classification_error(xgb_val_conf), "\n")

```

